
\cvsection{Experience}

\begin{cventries}
\cventry
    {Software Developer} % Job title
    {EPAM Systems} % Organization
    {Minsk, Belarus} % Location
    {Apr. 2018 - Now} % Date(s)
    {%Description
        \cvproject
            {Library Management System} % project name
            {C Developer} % position
            {GDB, C, Screen, SSH, VIM, AWS, Docker, CentOS}%Tech stack
            {
                \begin{cvitems}
                    \item {Debugged and maintained back-end of library management
                    system consisting mainly of legacy C code on remote machines. }
                    \item { Investigated problems and resolved them.}
                \end{cvitems}    
           }
        \cvproject
            {DNS Security System} % project name
            {Go Developer} % position
            {Go (Golang), Docker, GitHub, protobuf, REST, PostgreSQL}%Tech stack
            {
                \begin{cvitems}
                    \item {Developed and maintained gRPC/REST microservices.}
                    \item {Initiated development of request pre-processing module for protobuf, improving maintanability and 
                    ease of features development.}
                \end{cvitems}  
            }
        \cvproject
            {Industrial IoT Kit} % project name
            {C/C++ Developer} % position
            {C/C++, Valgrind, glibc, IAR toolkit, BLE, IoT}%Tech stack
            {
                \begin{cvitems}
                    \item {Development and testing industrial IoT sensors firmware and
                        improvement of integration with gateway.}
                    \item {Reduced firmware upgrade process time.}
                \end{cvitems} 
            }
    }

\cventry
    {Systems Engineer} % Job title
    {TSARKA} % Organization
    {Astana, Kazakhstan} % Location
    {Nov. 2016 - Mar. 2018} % Date(s)
    {%Description
        \cvproject % Usage: 
            {Wireless Networks Inspection Tool} % project name
            {Python Developer} % position
            {Python, aircrack-ng, RaspberryPi, SolidWorks, hashcat, telegram bot API}%Tech stack
            {
                \begin{cvitems}
                    \item {Implemented scannig and testing functionality and automated testing scenarios}
                    \item {Developed Control Interface for remote control via Telegram Bot API}
                    \item {Automated firmware upgrade routine}
                    \item {Designed in SolidWorks and 3D Printed case for the instrument}
                \end{cvitems}
            }
        \cvproject % Usage: 
            {Automated USB Pentest Tool} % project name
            {Electronics Engineer} % position
            {Python, C/C++, Tkinter, STM, Microchip, USB, SolidWorks, Kicad, Prototyping, Electronics Manufacturing}%Tech stack
            {
                \begin{cvitems}
                    \item {Electronic Circuit Design, to small scale PCB manufacture with component
                    soldering}
                    \item {Implemented firmware and integration with USB stack.}
                    \item {Developed cross-platform GUI client on Python + Tk.}
                \end{cvitems}
            }
    }

\cventry
    {Software Developer} % Job title
    {KazInfoSystems} % Organization
    {Astana, Kazakhstan} % Location
    {Jul. 2016 - Oct. 2016} % Date(s)
    {%Description
        \cvproject % Usage: 
            {Data management system of geoinformation of oil production sites} % project name
            {Fullstack Developer} % position
            {JavaScript, Ext.js , Java, maven}%Tech stack
            {
                \begin{cvitems}
                    \item {Developed file uploading module in ExtJS binding with service in Java EE}
                    \item {Fixed various bugs in submodules both on front- and back-end}
                \end{cvitems}
            }
    }
\hideblock{
\cventry
    {Electrical Engineer} % Job title
    {New ServiceArt} % Organization
    {Astana, Kazakhstan} % Location
    {Apr. 2016 - Jun. 2016} % Date(s)
    {%Description
        \cvproject % Usage: 
            {Telepresence Robot} % project name
            {Electronics Engineer} % position
            {C, Arduino, circuitry, sensors}%Tech stack
            {
                \begin{cvitems}
                    \item {Developed power management module and improved proximity sensors positioning}
                \end{cvitems}
            }
    }
}
\end{cventries}
